Important Factors in Predicting a Stroke

### 2021-05-13 draft.Rmd
some data analysis

---
title: "First Draft"
author: "Group 10"
output: 
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
---

@@

Being able to answer this question would provide many benefits. According to the CDC, strokes are one of the leading causes of death in the U.S. They are hard to deal with, and being able to predict and therefore prevent them would be useful. If high-risk individuals could be identified, they could also be informed of warning signs of stroke to look out for, as stroke survival rates are much higher when emergency treatment begins quickly.

@@

@@

@@

>>>>

---
title: "Important Factors in Predicting a Stroke"
author: "Group 10"
output: 
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
---

@@

Being able to answer this question would provide many benefits. According to the CDC, strokes are one of the leading causes of death in the U.S. The World Health Organization also reports stroke as one of the leading causes of death worldwide. They are hard to deal with, and being able to predict and therefore prevent them would be useful. If high-risk individuals could be identified, they could also be informed of warning signs of stroke to look out for, as stroke survival rates are much higher when emergency treatment begins quickly.

```{r fig.width=6, fig.height=6,echo=FALSE,fig.align="center"}
library(png)
library(grid)
img <- readPNG("death_worlwide.png")
 grid.raster(img)
```

@@

Exploratory data analysis is important for us to better understand this dataset before we go into deeper analysis. We want to identify the most important variables and variables that aren't as useful. We also want to identify possible outliers, missing values, and understand the relationship between variables. Ultimately, the goal is to maximize our insight of the dataset to minimize potential error that could occur later in the process.

#### First Glance

@@

A first look at the data:

```{r, echo = FALSE}
str(stroke)
```

-initial summary statistics

-which columns have missing values?

-look at correlations between variables
-heart disease and hypertension?

#### Variable Correlation

```{r, echo = FALSE, results = FALSE}
# Correlation 
stroke <- read.csv("stroke.csv")
stroke$bmi <- gsub("N/A", NA, stroke$bmi)
stroke$smoking_status <- gsub("Unknown", NA, stroke$smoking_status)
stroke <- na.omit(stroke)
stroke <- stroke[ -c(1)]
str(stroke)

stroke$gender <- as.factor(stroke$gender)
stroke$ever_married <- as.factor(stroke$ever_married)
stroke$work_type <- as.factor(stroke$work_type)
stroke$Residence_type <- as.factor(stroke$Residence_type)
stroke$smoking_status <- as.factor(stroke$smoking_status)

stroke <- lapply(stroke, function(x) as.numeric(x))

stroke <- as_tibble(stroke)

stroke_correlations <- cor(stroke)
datatable(stroke_correlations)
```

Something that would be interesting to look at would be the correlation between variables, to see if any of the variables vary in similar ways.

```{r, echo = FALSE, message = FALSE}
install.packages("corrplot")
library(corrplot)
corrplot(stroke_correlations, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

This is a visualization of the correlation plot, which confirms that no variables appear to be highly correlated with one another. The dark blue diagonal circles are just the variables correlated with themselves.

@@

https://towardsdatascience.com/exploratory-data-analysis-in-r-for-beginners-fe031add7072
